Preliminary Thesis Defence

### 2014-01-06 endnotes.tex
end notes

I believe that my South Africa paper provides an interesting opportunity to exploit the data from the household survey,
done before and after a highly relevant policy change.
Especially since the methodology and location are the same as in \textcite{duflo2000child, duflo2003grandmothers}.
In addition to this there is now a third data wave which has become available.
This provides us with more data, and mostly the opportunity to use more interesting methodology.
The text of the paper still has to be written.

The discussion of \textcite{morris1998unique} is in a very early stage.
I have looked at the paper in detail, I have also done a brief analysis of my main critique,
namely the conflation of risk (quantifiable) and Knightian uncertainty (unquantifiable).
However, I would like to present a worked out example which demonstrates how this convolution leads to the main result of the paper.
In addition to this, this example should demonstrate how only a part of the `ripe for attack' region is solved for the unique equilibrium.

Finally, relating to Bitcoin \parencite{nakamoto2008bitcoin}, I think that there is a enormous potential for uncontrolled low-cost remittances using Bitcoin. I would like to analyse the spread of this. I propose to follow the spread of applications for platforms which are popular in developing economies.

At this point, three out of four of the previously discussed research projects are some form of a replication of prior work. As replications they are mostly critiques of others' work, rather than constructive ideas. This is mostly a result of the fact that these projects progress faster. For this reason, these research projects have progressed more than the projects which are primarily based on my own ideas. However, it is my attention to shift the focus of my thesis to include more original work. Here I present two more ideas which are too preliminary to include in the main body of the text, but are based on my own work.

>>>>

The South Africa paper provides an interesting opportunity to exploit the data from the household survey,
done before and after a highly relevant policy change.
Especially since the methodology and location are the same as in \textcite{duflo2000child, duflo2003grandmothers}.
We find results that are highly relevant for the optimal design of cash transfer schemes.
At this point, the analysis is troubled by the non establishment of the common trend, prior to the treatment.
Using additional data or the control group this can be remedied, which will make the results more relevant still.

\textcite{morris1998unique} is analysed in detail.
The main issue is the conflation of risk (quantifiable) and Knightian uncertainty (unquantifiable).
However, there are two more issues in this paper which I also discuss, each of these invalidate the results.
However, I would like to present a worked out example which demonstrates how this convolution leads to the main result of the paper.
In addition to this, this example should demonstrate how only a part of the `ripe for attack' region is solved for the unique equilibrium.

Relating to Bitcoin \parencite{nakamoto2008bitcoin}, I present two ideas.
I think that there is a enormous potential for uncontrolled low-cost remittances using Bitcoin.
I would like to analyse the spread of this.
I propose to follow the spread of applications for platforms which are popular in developing economies.

Lastly, I present a proposal for a theoretical model on how cryptocurrencies gain momentum, this model can be extended to address two issues relating to Bitcoin, namely the supposed non-inflation, as well as the unlimited socially wasteful coin mining.

Here I present two more ideas which are too preliminary to include in the main body of the text.
